Compositional equivalences based on Open pNets

### 2020-04-21 2016-Weak-FH-Bisim/WeakBisim.tex
sectionning in the appendix

\newpage
\appendix

       \section{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}\label{thm-equiv-proof}
        \emph{Suppose $\mathcal{R}$ 
       	is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, 
       	$\mathcal{R}$ is 
       	reflexive, symmetric and transitive.
       	}
%%% A PROOF WITH CONSTRUCTIVE AERGUMENTS BUT THAT DOES NOT WORK

@@

       \section{Proofs of properties on pNets}
\subsection{Composition Lemmas}       
       The proof of the other theorems rely on two main lemmas,
dealing respectively with the decomposition of a composed behaviour
between the context and the internal pNet, and with their recomposition.

\paragraph{Lemma~\ref{lem-decompose}}: {\bf Open transition decomposition} \\
 Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\beta_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred \iff \Pred\,'
		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$\Leaves(Q)$.

@@

\paragraph{\bf Lemma~\ref{lem-compose}} {\it Open transition composition}\\
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~~and~~}
%\[
Q\models{\openrule
	{
		\beta_j^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]

@@

\begin{lemma}[Open transition composition -- inactive]\label{lem-compose-2} ~\\	This lemma is the simple case where the pNet filling the hole is not involved in the transition. Suppose $j_0\not\in J$ and $L_Q=\Leaves({Q})$:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\beta_j^{j\in J}, 
			\Pred,  
			\Post}
		{\ostate{s_i^{i\in L}\uplus s_i^{i\in L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L}\uplus s_i^{i\in L_Q}}}}
	\]
\end{lemma}
The proof is trivial.

>>>>

\newpage
\appendix    
\section{Proof on FH-bisimulation}
\subsection{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}\label{thm-equiv-proof}~\\
        \emph{Suppose $\mathcal{R}$ 
       	is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, 
       	$\mathcal{R}$ is 
       	reflexive, symmetric and transitive.
       	}
%%% A PROOF WITH CONSTRUCTIVE AERGUMENTS BUT THAT DOES NOT WORK

@@

\subsection{Composition Lemmas}       
       The proofs of the composition theorems for FH-bisimulation rely on two main lemmas,
dealing respectively with the decomposition of a composed behaviour
between the context and the internal pNet, and with their recomposition.

\subsubsection*{{\bf Lemma~\ref{lem-decompose}}: Open transition decomposition} ~\\
 Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\beta_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred \iff \Pred\,'
		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$\Leaves(Q)$.

@@

\subsubsection*{ \bf{Lemma~\ref{lem-compose}}:  Open transition composition}~\\
	Suppose $j_0\in J$ and:\\[-1ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~~and~~}
%\[
Q\models{\openrule
	{
		\beta_j^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]

@@

\begin{lemma}[Open transition composition -- inactive]\label{lem-compose-2} ~\\	This lemma is the simple case where the pNet filling the hole is not involved in the transition. Suppose $j_0\not\in J$ and $L_Q=\Leaves({Q})$:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\end{mathpar}
Then, we have\\[-1ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\beta_j^{j\in J}, 
			\Pred,  
			\Post}
		{\ostate{s_i^{i\in L}\uplus s_i^{i\in L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L}\uplus s_i^{i\in L_Q}}}}
	\]
\end{lemma}
The proof is trivial.
